Advice on describing Bayesian analysis of neutron and X-ray reflectometry

### 2022-11-11 src/tex/ms.tex
Remove DMSC
Typo

% Author list
\author{Andrew R. McCluskey}
  \email{andrew.mccluskey@ess.eu}
  \affiliation{Data Management and Software Centre, European Spallation Source ERIC, 2200 K{\o}benhavn, DK}
  \affiliation{European Spallation Source ERIC, P.O. Box 176, SE-221 00, Lund, SE}
\author{Andrew J. Caruana}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Christy J. Kinane}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Alexander J. Armstrong}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Tom Arnold}
  \affiliation{European Spallation Source ERIC, P.O. Box 176, SE-221 00, Lund, SE}
\author{Joshaniel F. K. Cooper}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{David L. Cortie}
  \affiliation{Australian Nuclear Science and Technology Organisation, Lucas Heights, New South Wales, AU}  
\author{Arwel V. Hughes}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Jean-Fran\c{c}ois Moulin}
  \affiliation{German Engineering Material Science at Heinz Maier-Leibnitz Zentrum, Helmholtz-Zentrum Hereon, Lichtenbergstraße 1, 85748 Garching, DE}
\author{Andrew R. J. Nelson}
  \affiliation{Australian Nuclear Science and Technology Organisation, Lucas Heights, New South Wales, AU}  
\author{Wojciech Potrzebowski}
  \affiliation{Data Management and Software Centre, European Spallation Source ERIC, 2200 K{\o}benhavn, DK}
  \affiliation{European Spallation Source ERIC, P.O. Box 176, SE-221 00, Lund, SE}
\author{Vladimir Starostin}
  \affiliation{Institute of Applied Physics, University of T\"{u}bingen, Auf der Morgenstelle 10, 72076 T\"{u}bingen, DE}

@@

The optimised parameters from the minimisation algorithm, which depend on the particular algorithm, often include some statistical uncertainty.
This uncertainty comes from an assumption of normally distributed parameters \cite{bevington_data_2002}, however, Bayesian sampling approaches make no assumption of an underlying statistical distribution.
How these statistical uncertainties are found is beyond the scope of this work, but it is important to acknowledge that this uncertainty typically assumes that the probability distribution of the parameter is Gaussian in nature. 
This probability distribution is either the partial likelihood or posterior, the latter when some prior is included and Bayes theorem is applied. The posterior describes our understanding of the parameter values given the data that was measured.
When Bayesian modelling is used and the prior is included, the posterior probability is found as, 
%
\begin{equation}
  p(\mathbf{x} | \mathbf{D}) \propto p(\mathbf{D} | \mathbf{x}) p(\mathbf{x}).
  \label{equ:bayes}
\end{equation}
%
Therefore, when Bayesian modelling is performed, the priors and likelihood are of fundamental importance to the results that are obtained (the posterior), and any scientific conclusions that are drawn. 
We note that Equation~\ref{equ:bayes} omits the normalisation term, the Bayesian evidence [$p(\mathbf{D})$], which is discussed in detail elsewhere \cite{sivia_bayesian_1998,mccluskey_general_2020} and can be omitted when model comparison is not begin performed.

>>>>

% Author list
\author{Andrew R. McCluskey}
  \email{andrew.mccluskey@ess.eu}
  \affiliation{European Spallation Source ERIC, P.O. Box 176, SE-221 00, Lund, SE}
\author{Andrew J. Caruana}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Christy J. Kinane}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Alexander J. Armstrong}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Tom Arnold}
  \affiliation{European Spallation Source ERIC, P.O. Box 176, SE-221 00, Lund, SE}
\author{Joshaniel F. K. Cooper}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{David L. Cortie}
  \affiliation{Australian Nuclear Science and Technology Organisation, Lucas Heights, New South Wales, AU}  
\author{Arwel V. Hughes}
  \affiliation{ISIS-Neutron and Muon Source, Rutherford Appleton Laboratory, Didcot, Oxon OX11 0QX, GB}
\author{Jean-Fran\c{c}ois Moulin}
  \affiliation{German Engineering Material Science at Heinz Maier-Leibnitz Zentrum, Helmholtz-Zentrum Hereon, Lichtenbergstraße 1, 85748 Garching, DE}
\author{Andrew R. J. Nelson}
  \affiliation{Australian Nuclear Science and Technology Organisation, Lucas Heights, New South Wales, AU}  
\author{Wojciech Potrzebowski}
  \affiliation{European Spallation Source ERIC, P.O. Box 176, SE-221 00, Lund, SE}
\author{Vladimir Starostin}
  \affiliation{Institute of Applied Physics, University of T\"{u}bingen, Auf der Morgenstelle 10, 72076 T\"{u}bingen, DE}

@@

The optimised parameters from the minimisation algorithm, which depend on the particular algorithm, often include some statistical uncertainty.
This uncertainty comes from an assumption of normally distributed parameters \cite{bevington_data_2002}, however, Bayesian sampling approaches make no assumption of an underlying statistical distribution.
How these statistical uncertainties are found is beyond the scope of this work, but it is important to acknowledge that this uncertainty typically assumes that the probability distribution of the parameter is Gaussian in nature. 
This probability distribution is either the partial likelihood or posterior, the latter when some prior is included and Bayes theorem is applied. The posterior describes our understanding of the parameter values given the data that was measured.
When Bayesian modelling is used and the prior is included, the posterior probability is found as, 
%
\begin{equation}
  p(\mathbf{x} | \mathbf{D}) \propto p(\mathbf{D} | \mathbf{x}) p(\mathbf{x}).
  \label{equ:bayes}
\end{equation}
%
Therefore, when Bayesian modelling is performed, the priors and likelihood are of fundamental importance to the results that are obtained (the posterior), and any scientific conclusions that are drawn. 
We note that Equation~\ref{equ:bayes} omits the normalisation term, the Bayesian evidence [$p(\mathbf{D})$], which is discussed in detail elsewhere \cite{sivia_bayesian_1998,mccluskey_general_2020} and can be omitted when model comparison is not being performed.
